Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-05 sections/tensors.tex
done with 3

\subsubsection{Scalars}
Because leaf levels are geared towards representing multiple leaves, we also introduce a much simpler Scalar format to represent 0-dimensional tensors.
%
Scalars don't have as much structure as clearly only two structures apply.
%
Through these structures, scalars can also affect other tensors in crucial ways.
%
Constant propagation through arrays is known to be a complex compiler pass \cite{mcmichen_representing_nodate}.
%
Instead, we provide sparse scalars, which allow reductions but also specialize read accesses for the possible zero value.
%
We also provide early break scalars, which modify the stepper Looplets to
re-specialize the loop whenever a reduction into an early break scalar hits an
annihilator.
%
We assume that we don't need to re-specialize other Looplets because the stepper
is the only one which repeats a non-constant number of times.

@@

>>>>

@@

\subsubsection{Scalars}
Because leaf levels are geared towards representing multiple leaves, we also introduce a much simpler Scalar format to represent 0-dimensional tensors.
%
Scalars don't have as much structure as clearly only two structures apply.
%
Through these structures, scalars can also affect other tensors in crucial ways.
%
Constant propagation through arrays is known to be a complex compiler pass \cite{mcmichen_representing_nodate}.
%
Instead, we provide sparse scalars, which allow reductions but also specialize read accesses for the possible zero value.
%
We also provide early break scalars, which modify the stepper Looplets to
re-specialize the loop whenever a reduction into an early break scalar hits an
annihilator.
%
We don't need to re-specialize other Looplets because the stepper
is the only one which repeats a non-constant number of times.
%
We represent early break as a structural property rather than a program node
because it allows us to represent the tail of a loop where one scalar has hit an
annihlator but another scalar hasn't.
%
To our knowlege, sparse and early break scalars are novel contributions of this
work; other systems don't include them, limiting the impact of sparsity.
